---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rbooty

<!-- badges: start -->
<!-- badges: end -->

rbooty provides comprehensive functions for bootstrapping.

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("lana1218/rbooty")
```

```{r}
library(rbooty)
```


## Summarizing the bootsrap distribution

* `bs_summarize()` allows you to output the summary statistics and resulting bootstrap distribution in one output, given a desired statistic (mean, median, quantile, sd, iqr)

```{r}
library(rbooty)

test <- bootstrap(tips$TipPercent, stat = "mean")

bs_summarize(tips$TipPercent, stat = "mean")
```

## Other Use Cases
You can calculate the statistics for the bootstrap distribution independently.

```{r}
bs_loc_stat(tips, stat = "med")

bs_scale_stat(tips, stat = "sd")
```

You can also get a dataframe of the bootstrap distribution. 

```{r}

```

